Delocalization of Eigenvectors in Random Matrices

### 2025-03-24 Draft.tex
Corollary B5

>>>>

\begin{boxtheorem}{Corollary B5}\label{corollary-b5} - Let $\mathcal{A}$ be an even on which the following holds for all $t\in [0, 1]$: $$\max_{a, b}\left(S^{1/2}T_t(z)S^{1/2}\right)_{ab}\lesssim W^{-1}\eta_t^{-1/2}$$
Then, we have the following stochastic bound for any large $C>0$ that is independent of $W$: $$\mathbf{1}_{\mathcal{A}}\max_{t\in [0, 1]} \max_{x, y}\frac{|G_{xy} - \delta_{xy}m(z)|}{(S^{1/2}T_t(z)S^{1/2})_{ab}+S^{1/2}_{ab}+W^{-C}}\prec 1$$
.
\end{boxtheorem}
\textit{Proof} - the result follows by Lemmas B.3 and B.4 from a continuity argument. Can be found as Corollary 14 in \cite{bandSDE}
